Airbnb Predictions Project

### 2019-01-03 content/post/article.Rmd

---
title: "Airbnb Predictions Project"
author: "Effi Feldblum"
date: '2018-12-10'
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]

>>>>

---
title: Airbnb Predictions Project
author: Effi Feldblum
slug: airbnb
description: A short Article
date: '2018-12-10'
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
